Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2023-07-21 src/sections/intro.tex

{\color{blue} NGC 2808 is the prototype globular cluster to host Multiple
Populations.} Various studies since 2007 have identified that it may host
anywhere from 2-5 stellar populations. These populations have been identified
both spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}.
Note that recent work \citep{Valle2022} calls into question the statistical significance
of the detections of more than 2 populations in the spectroscopic data. Here we
present new, chemically self-consistent modeling of the two extreme populations
of NGC 2808 identified by \citet{Milone2015}, populations A and E.
{\color{blue} Additionally, we present a likelihood analysis of the photometric
data of NGC 2808 to determine the number of populations present in the cluster.}

>>>>

{\color{blue} NGC 2808 is the prototype globular cluster to host Multiple
Populations.} Various studies since 2007 have identified that it may host
anywhere from 2-5 stellar populations. These populations have been identified
both spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}.
Note that recent work \citep{Valle2022} calls into question the statistical significance
of the detections of more than 2 populations in the spectroscopic data. Here we
present new, chemically self-consistent modeling of the photometry of the two extreme populations
of NGC 2808 identified by \citet{Milone2015}, populations A and E.
{\color{blue} Additionally, we present a likelihood analysis of the photometric
data of NGC 2808 to determine the number of populations present in the cluster.}
